---
title: "README"
output: 
  github_document:
    toc: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = ">")
```

##  READ ME

This **README** file gives a detailed description fo the contents of this folder/repo, and things to do to enable a smooth workflow. Endeavour to read this.

```{r, echo=FALSE}

readme <- data.frame(No = 1:9, 
           Item = c("*Dates of the surveys*", "*Survey Title*", "*Associated files*", "*Summary*",
                    "*Key words*", "*People involved*", "*Short description of survey design*", 
                    "*Data format*", "*Associated projects*"), 
           Description = c("17/03/2020, 25/03/2020", "Hoe ga je om met coronoa?", 
                           " README.md, masterFile.Rmd, plots, RImages, RScripts", 
                           "A survey on peoples perception about COVID19", 
                           "COVID-19, contact",
                           "**Neyens Thomas (NYT)**
                           **<br> Olusoji Oluwafemi Daniel (DOO)** 
                           **<br> Aerts Marc (MRA)**
                           **<br> Others, I cannot name for now**", 
                           "A sample of the Belgian population filled the survey via Facebook", 
                           "**SPSS sav files in folders stored on google drive**"
                           , "Other projects going on using the same data"
                           )
           )
pander::pander(readme, keep.line.breaks = TRUE, style = 'grid', justify = 'left')
```

## Steps

1. Clone this repo by running `git clone https://github.com/fomotisUhasselt/COVID19Survey.git` in git bash or simply click on the `clone` option in the `Repository` tab, if you use Git GUI.

2. Double click on COVID19Survey.Rproj in the repo. This should open up RStudio with the COVID19Survey project.

3. Create your own branch within the repo by running `git checkout -b your_branch_name_here` in the RStudio Terminal (the tab for this is besides the Console tab).

4. Do your thing in the `masterFile.Rmd` file. Remember to create a section for your analysis. Step 3 makes sure that you are not editing the original file directly, rather you edit a copy in your branch.

4. After every analysis or at the end of a day's job:

    a. add changes made to your branch by running `git add .` 

    b. commit changes to your branch by running `git commit -m "a short descritptive message of what you did here"`
  
    c. push changes made to your branch by running `git push origin your_branch_name_here`
  
    d. create a pull request for your changes to be added to the master file by clicking on the `pull requests`, and `new pull request tab` tab on Github.

5. Your pull request will be merged later and this updates the original `masterFile.Rmd`.  

## Note

It is safer for each of us to create branches and work with our individual branches. After finishing any analysis, you can create a pull request for it to be merged with the master. Doing this allows easy tracing of errors.




